### 2024-08-26 paper.tex
more of intro and organization

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
Let
\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
\par Let
\[e = \begin{pNiceArray}{ccccc}
 0 \\
    1 & 0 \\
  & 1 & \ddots \\
   & & \ddots & 0 \\
   &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{gl}_{n},\]
and let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).

\begin{lemma}\label{simple_sl2_triple}
    There is exactly one way to choose \(h, f \in \gl_n\) so that \((e, h, f)\) is an \(\spl_2\)-triple.
\end{lemma}
\begin{proof}

@@

@@

\section{A different variety}
Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
We will verify these things using our prvious computations of springer fibers.

>>>>

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
Let
\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In this paper we will study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\section{Principal \(\spl_2\)-triple in \(\gl_n\)}
The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
In this section we use this to find that there is a unique principal \(\spl_2\)-triple in \(\gl_n\).
Write \(e = J_n\).
\begin{lemma}\label{simple_sl2_triple}
    There is exactly one way to choose \(h, f \in \gl_n\) so that \((e, h, f)\) is an \(\spl_2\)-triple.
\end{lemma}
\begin{proof}

@@

\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
TODO: I am unsure why this section is interesting or what to say about it.
Should I delete it?
For now I will ignore it and try to make the paper flow nicely without it.

Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
% First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).

@@

\section{The components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
We will verify these things using our prvious computations of springer fibers.
